---
title: "p8105_hw6_cr3442"
author: "Cheng Rao"
date: "2024-12-02"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(cowplot)
library(patchwork)
library(modelr)
library(p8105.datasets)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "100%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
set.seed(2844)
```

# Problem 1

First import the data.
\
```{r rnoaa_import, include = F , cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
\
Then take a look of the regression.
\
```{r rnoaa_reg}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm",se = F)
```
\

Let's bootstraping.
\
```{r bootstrap,cache = T}
weather_boot = 
  weather_df %>% 
  bootstrap(n = 5000) %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy),
    glanced = map(models, broom::glance)
    ) %>% 
  select(-strap, -models) %>% 
  unnest(c(results, glanced), names_repair = "unique") %>% 
  select(.id, term, estimate, r.squared) %>% 
  mutate(
    term = str_replace(term, "\\(Intercept\\)", "intercept")
  ) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  mutate(
    intersection = log(intercept * tmin),
    .id = as.numeric(.id)
  ) %>% 
  select(-intercept, -tmin)
```

Let's plot the distribution of r square.
\
```{r rsquare_plt}
weather_boot %>% 
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(
    title = "Distribution of Estimates of R-squared",
    x = "R-square estimates",
    y = "Density"
  ) +
  scale_x_continuous(
    breaks = seq(.85,.95,.01)
  )

```
\
Let's plot the distribution of intersection, while intersection = log(β0 * β1).
\
```{r}
weather_boot %>% 
  ggplot(aes(x = intersection)) +
  geom_density() +
  labs(
    title = "Distribution of Estimates of Coefficients Intersections",
    x = "Coefficients Estimates Intersection",
    y = "Density"
  ) +
  scale_x_continuous(
    breaks = seq(1.90, 2.15, .02)
  )
```
\
Finally, lets calculate and report the 95% confidence interval.
\
```{r}
ci_r_squared = quantile(weather_boot$r.squared, c(0.025, 0.975))
ci_intersection = quantile(weather_boot$intersection, c(0.025, 0.975))

ci_r_squared
ci_intersection
```

**Comments:**
\
The distribution of estimated r-squared is approximately normal. With the mean `r mean(weather_boot$r.squared)` and median `r median(weather_boot$r.squared)`. And the standard error of this distribution is `r sd(weather_boot$r.squared)`. Ranging from `r min(weather_boot$r.squared)` to `r max(weather_boot$r.squared)`.
\
\
The distribution of the natural log of the intersection of estimated coefficients is approximately normal. With the mean `r mean(weather_boot$intersection)` and median `r median(weather_boot$intersection)`. And the standard error of this distribution is `r sd(weather_boot$intersection)`. Ranging from `r min(weather_boot$intersection)` to `r max(weather_boot$intersection)`.
\
\
 With 95% confidence, the r-squared value, which measures the goodness of fit of the regression model, lies between 0.894 and 0.927.  With 95% confidence, the value of log(β0 * β1), which reflects the logarithm of the product of the intercept and slope coefficients, lies between 1.96 and 2.06.

