---
title: "p8105_hw6_cr3442"
author: "Cheng Rao"
date: "2024-12-02"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(cowplot)
library(patchwork)
library(modelr)
library(p8105.datasets)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "100%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
set.seed(2844)
```

# Problem 1

First import the data.
\
```{r rnoaa_import, include = F , cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
\
Then take a look of the regression.
\
```{r rnoaa_reg}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm",se = F)
```
\

Let's bootstraping.
\
```{r bootstrap,cache = T}
weather_boot = 
  weather_df %>% 
  bootstrap(n = 5000) %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy),
    glanced = map(models, broom::glance)
    ) %>% 
  select(-strap, -models) %>% 
  unnest(c(results, glanced), names_repair = "unique") %>% 
  select(.id, term, estimate, r.squared) %>% 
  mutate(
    term = str_replace(term, "\\(Intercept\\)", "intercept")
  ) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  mutate(
    intersection = log(intercept * tmin),
    .id = as.numeric(.id)
  ) %>% 
  select(-intercept, -tmin)
```

Let's plot the distribution of r square.
\
```{r rsquare_plt}
weather_boot %>% 
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(
    title = "Distribution of Estimates of R-squared",
    x = "R-square estimates",
    y = "Density"
  ) +
  scale_x_continuous(
    breaks = seq(.85,.95,.01)
  )

```
\
Let's plot the distribution of intersection, while intersection = log(β0 * β1).
\
```{r}
weather_boot %>% 
  ggplot(aes(x = intersection)) +
  geom_density() +
  labs(
    title = "Distribution of Estimates of Coefficients Intersections",
    x = "Coefficients Estimates Intersection",
    y = "Density"
  ) +
  scale_x_continuous(
    breaks = seq(1.90, 2.15, .02)
  )
```
\
Finally, lets calculate and report the 95% confidence interval.
\
```{r}
ci_r_squared = quantile(weather_boot$r.squared, c(0.025, 0.975))
ci_intersection = quantile(weather_boot$intersection, c(0.025, 0.975))

ci_r_squared
ci_intersection
```

**Comments:**
\
The distribution of estimated r-squared is approximately normal. With the mean `r mean(weather_boot$r.squared)` and median `r median(weather_boot$r.squared)`. And the standard error of this distribution is `r sd(weather_boot$r.squared)`. Ranging from `r min(weather_boot$r.squared)` to `r max(weather_boot$r.squared)`.
\
\
The distribution of the natural log of the intersection of estimated coefficients is approximately normal. With the mean `r mean(weather_boot$intersection)` and median `r median(weather_boot$intersection)`. And the standard error of this distribution is `r sd(weather_boot$intersection)`. Ranging from `r min(weather_boot$intersection)` to `r max(weather_boot$intersection)`.
\
\
 With 95% confidence, the r-squared value, which measures the goodness of fit of the regression model, lies between 0.894 and 0.927.  With 95% confidence, the value of log(β0 * β1), which reflects the logarithm of the product of the intercept and slope coefficients, lies between 1.96 and 2.06.


# Problem 2

First import the data and clean it up.
\
```{r read_homicide}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("","NA","Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolved = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1
    )
  ) %>% 
  select(city_state, victim_age, victim_race, victim_sex,resolved) %>% 
filter(
  victim_race %in% c("White", "Black"),
  city_state != "Dallas, TX" & 
  city_state != "Phoenix, AZ" & 
  city_state != "Kansas City, MO" & 
  city_state != "Tulsa, AL"
)
```
\
Start with one sample city, Baltimore.
\
```{r one_city}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolved ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```
\
Then perform batch analysis for each city.
\
```{r map_to_cities}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = .x,family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state,term,OR,starts_with("CI"))
```
\
Finally, plot the OR and CI of each city.
\
```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>%      
  mutate(
    city_state = fct_reorder(city_state, OR)   
  ) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2) + 
  geom_point() +                                                     
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +     
  theme_minimal() +                                                   
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1),                 
    plot.title = element_text(size = 14, face = "bold"),              
    plot.subtitle = element_text(size = 10)                          
  ) +
  labs(
    x = "City, State",                                                
    y = "Adjusted Odds Ratio (OR)",                                    
    title = "Adjusted Odds Ratios (Male vs Female) by City",          
    subtitle = "Error bars represent 95% confidence intervals",        
    caption = "Data Source: The Washington Post Homicide Dataset"     
  )
```

**Comments:**
\
The red dashed line (OR = 1) is the reference line, indicating that male and female victims are equally likely to have their cases resolved. Most cities have confidence intervals that include OR = 1, indicating that gender differences in these cities are not statistically significant. 
\
However, the adjusted odds ratios (ORs) for different cities range widely, from close to 0 to over 3, showing significant differences in gender differences between cities. In cities where the OR is significantly lower than 1 (such as some cities on the far left, such as New York, NY), it indicates that female victims have a higher likelihood of having their cases resolved. In cities where the OR is significantly higher than 1 (such as Albuquerque, NM and Stockton, CA on the far right), male victims have a higher likelihood of having their cases resolved. However, in some cities, the confidence intervals are wide, which may reflect insufficient sample size or unstable data. 
\
But overall, male victims are slightly less likely to have their cases resolved than female victims.
